The Error Estimate of Short-Range Force Calculation in the Inhomogeneous Molecular Systems

### 2012-07-23 shortRange.inhomo/alltext/pubilsh.pre/resubmit/main.tex
add resubmit

\begin{figure}
  \centering
  \includegraphics[]{error.uniform.eps}
  \caption{The RMS force error distribution of the 16000 Lennard-Jones
    particle system at $T^\ast=0.85$ with a uniform cut-off radius of
    $r_c^\ast = 7.5$. The green squares present the real error. The
    solid blue line is the error estimate by \eqref{eqn:tmp5}. The
    dashed blue line is the homogeneity error contribution, while the
    dotted blue line is the inhomogeneity error contribution. The
    density distribution of the system is presented by red solid line
    for reference.  All properties are properly averaged on the $y$
    and $z$ direction, therefore, the profiles are plotted along the
    $x$ direction.  }
  \label{fig:tmp2}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{rcut.and.error.eps}
  \caption{ The RMS force error distribution of the 16000
    Lennard-Jones particle system at $T^\ast=0.85$ with adaptive
    cut-off radius. The control error $\mathcal E^\ast_{\textrm{C}}$
    is the same as the maximum error in the uniform cut-off simulation
    with $r_c^\ast=7.5$.  The resulting cut-off radius distribution is
    presented by the red line. All other notations are the same as
    Fig.~\ref{fig:tmp2}.}
  \label{fig:tmp3}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{fcorr.and.error.eps}
  \caption{ The RMS force error distribution of the 16000
    Lennard-Jones particle system at $T^\ast=0.85$ with long-range
    force correction, i.e. eqn. \eqref{eqn:define-fcorr}. The cut-off
    radius is $r^\ast_c = 7.5$. The $x$ component of the correction
    force is presented by the solid red line. The green squares
    present the real error. The solid blue line presents the estimated
    homogeneity error. }
  \label{fig:tmp4}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{t0.85.gas.eps} 
  \includegraphics[width=0.49\textwidth]{t0.85.liquid.eps} 
  \caption{$T^\ast = 0.85$. The convergence of the equilibrium gas and
    liquid densities with respect to the cut-off radius. All densities
    are compared with the reference value (black solid line), namely,
    the liquid and vapor densities measured with a uniform cut-off
    radius $r_c^\ast=13$. The gray region denotes the statistical
    uncertainty of the reference value.  This figure presents the
    results of three methods, namely the uniform cut-off (URC), the
    adaptive cut-off (ARC) and the force correction (LFC) method. }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{tension.t0.85.eps} 
  \caption{$T^\ast = 0.85$. The convergence of the surface tension
    with respect to the cut-off radius.  This figure presents the
    results of three methods, namely the uniform cut-off (URC), the
    adaptive cut-off (ARC) and the long-range force correction (LFC)
    method.  The results with and without long-range pressure
    correction (LPC) are shown together for comparison. The reference
    surface tensions, shown by solid black lines, are measured by the
    uniform cut-off method with $r_c^\ast=13$ using LPC.}
  \label{fig:tmp6}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{init.2.eps}
  \caption{The initial setup of cluster $A$ and $B$. The initial
    velocity are equal in magnitude but on opposite direction.}
  \label{fig:tmp7}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{trajs.eps}
  \caption{The center of mass trajectory of cluster A. Uniform cut-off
    (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC) $r_c =
    5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$ are
    investigated.  The time interval between two neighboring squares
    on the trajectory is 4.  }
  \label{fig:tmp8}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[]{dists.eps}
  \caption{The COM distance between cluster $A$ and cluster $B$ versus
    time. Uniform cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive
    cut-off (ARC) $r_c = 5.0$ and long-range force correction (LFC)
    $r^\ast_c = 2.5$ are investigated.  }
  \label{fig:tmp9}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.90\textwidth]{error-rcut-ball.eps} 
  \includegraphics[width=0.90\textwidth]{error-rcut.eps}
  \caption{The colliding clusters (the first row), the RMS force error
    distribution of uniform cut-off with $r_c^\ast = 5.0$ (the second
    row), the cut-off distribution of adaptive cut-off with $r_c^\ast
    = 5.0$ (the third row) and the magnitude of long-range force
    correction with $r_c^\ast = 2.5$ (the fourth row). The four
    columns corresponds to snap shots taken at $t^\ast = 12,\ 24,\
    36,\ 56$, respectively.  }
  \label{fig:tmp10}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{wy.eps}
  \caption{The angular velocity of cluster $A$ versus time. Uniform
    cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
    $r_c = 5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$
    are investigated.}
  \label{fig:tmp11}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[]{ly.eps}
  \caption{The angular moment of cluster $A$ versus time. Uniform
    cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
    $r_c = 5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$
    are investigated.}
  \label{fig:tmp12}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{cost.eps}
  \caption{The computational cost versus time. Uniform
    cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
    $r_c = 5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$
    are investigated.}
  \label{fig:tmp13}
\end{figure}

@@

In this paper, we developed the force error estimate for non-bonded
short-range interactions in the inhomogeneous molecular systems. The
RMS force error can be expressed by a summation of a homogeneity
error, an inhomogeneity error and a correlation error. In the present
paper, we only considered the cases, in which the correlation error
does not dominate. In an inhomogeneous system, the basic observation
of the error distribution was that the homogeneity error dominates the
bulk material regions, whereas the inhomogeneity error dominates the
interfacial regions where the density changes within the length scale
of a few molecules. The inhomogeneity error can be more than one
order of magnitude larger than the homogeneity error.  Two methods
were proposed to improve the efficiency and accuracy of the
simulation. The adaptive cut-off method uses smaller cut-off radius
for the low-error bulk regions and larger cut-off radius for the
high-error interfacial regions, so that the RMS force error is
uniformly distributed over the simulation region. The long-range force
correction method corrects the force computation by the mean error
force, so that the inhomogeneity error is removed from the system.

@@

{
  We want to stress again the main research interest of the present paper is the
  error estimate, the proposed adaptive cut-off and long-range
  correction methods. The examples are used to demonstrate
  the validity of these theoretical results. The applications
  of the error estimate is more general than the studied examples,
  because we only assumed the interaction is short-ranged and
  treated by the cut-off method.
  Other kind the short-range interaction (not only the Lennard-Jones
  but also the Buckingham,
  the direct part of the Ewald family algorithms, etc.),
  and other kinds of inhomogeneity
  (not only  planar and merging spherical interfaces)
  can be easily studied by the error estimates and the proposed methods.
  However, it is impossible to test all possible cases within one paper.
  The error study of
  more realistic systems requires the error estimates of the long-range
  algorithms, and careful comparisons with the short-range error.
  Since the present paper is focusing on the short-range
  interactions, and the space is limited,
  they will be given in the future work.
}

>>>>

\begin{figure}
  \centering
  \includegraphics[]{error.uniform.eps}
  \caption{(Color online)
    The RMS force error distribution of the 16000 Lennard-Jones
    particle system at $T^\ast=0.85$ with a uniform cut-off radius of
    $r_c^\ast = 7.5$. The green (light gray) squares present the real error. The
    solid blue (dark gray) line is the error estimate by \eqref{eqn:tmp5}. The
    dashed blue (dark gray) line
    is the homogeneity error contribution, while the
    dotted blue (dark gray) line
    is the inhomogeneity error contribution. The
    density distribution of the system is presented by red (middle gray)
    solid line
    for reference.  All properties are properly averaged on the $y$
    and $z$ direction, therefore, the profiles are plotted along the
    $x$ direction.  }
  \label{fig:tmp2}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{rcut.and.error.eps}
  \caption{ (Color online)
    The RMS force error distribution of the 16000
    Lennard-Jones particle system at $T^\ast=0.85$ with adaptive
    cut-off radius. The control error $\mathcal E^\ast_{\textrm{C}}$
    is the same as the maximum error in the uniform cut-off simulation
    with $r_c^\ast=7.5$.  The resulting cut-off radius distribution is
    presented by the red (middle gray) line. All other notations are the same as
    Fig.~\ref{fig:tmp2}.}
  \label{fig:tmp3}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{fcorr.and.error.eps}
  \caption{ (Color online)
    The RMS force error distribution of the 16000
    Lennard-Jones particle system at $T^\ast=0.85$ with long-range
    force correction, i.e. eqn. \eqref{eqn:define-fcorr}. The cut-off
    radius is $r^\ast_c = 7.5$. The $x$ component of the correction
    force is presented by the solid red (middle gray) line.
    The green (light gray) squares
    present the real error. The solid blue (dark gray)
    line presents the estimated
    homogeneity error. }
  \label{fig:tmp4}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{t0.85.gas.eps} 
  \includegraphics[width=0.49\textwidth]{t0.85.liquid.eps} 
  \caption{(Color online)
    $T^\ast = 0.85$. The convergence of the equilibrium gas and
    liquid densities with respect to the cut-off radius. All densities
    are compared with the reference value (black solid line), namely,
    the liquid and vapor densities measured with a uniform cut-off
    radius $r_c^\ast=13$. The gray region denotes the statistical
    uncertainty of the reference value.  This figure presents the
    results of three methods,
    namely the uniform cut-off (URC) in red (middle gray), the
    adaptive cut-off (ARC) in green (light gray)
    and the force correction (LFC) method in blue (dark gray).
    The cut-off of
    the adaptive cut-off method is $r_c^\ast$ means its
    control error is the maximum error of a uniform cut-off simulation
    using that cut-off $r_c^\ast$.
    Under this setting,  the maximum 
    cut-off radius of the adaptive cut-off method is the same as,
    or sometimes marginally larger  than
    $r_c^\ast$ (no more than $r_c^{\textrm{{step}}}$).
  }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{tension.t0.85.eps} 
  \caption{(Color online)
    $T^\ast = 0.85$. The convergence of the surface tension
    with respect to the cut-off radius.  This figure presents the
    results of three methods,
    namely the uniform cut-off (URC) in red (middle gray),
    the adaptive cut-off (ARC) in green (light gray)
    and the long-range force correction (LFC) method in blue (dark gray).
    The results with and without long-range pressure
    correction (LPC) are shown together for comparison. The reference
    surface tension, shown by the solid black line, is measured by the
    uniform cut-off method with $r_c^\ast=13$ using LPC.
    The cut-off of
    the adaptive cut-off method is $r_c^\ast$ means its
    control error is the maximum error of a uniform cut-off simulation
    using that cut-off $r_c^\ast$.
    Under this setting,  the maximum 
    cut-off radius of the adaptive cut-off method is the same as,
    or sometimes marginally larger  than
    $r_c^\ast$ (no more than $r_c^{\textrm{{step}}}$).
    % This setting leads to a maximum 
    % cut-off radius that is almost the same as $r_c^\ast$.
  }
  \label{fig:tmp6}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{init.2.eps}
  \caption{
    (Color online)
    The initial setup of cluster $A$ and $B$. The initial
    velocity are equal in magnitude but on opposite direction.}
  \label{fig:tmp7}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{trajs.eps}
  \caption{(Color online)
    The center of mass trajectory of cluster A. Uniform cut-off
    (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC) $r_c =
    5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$ are
    investigated.  The time interval between two neighboring squares
    on the trajectory is 4.  }
  \label{fig:tmp8}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[]{dists.eps}
  \caption{(Color online)
    The COM distance between cluster $A$ and cluster $B$ versus
    time. Uniform cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive
    cut-off (ARC) $r_c = 5.0$ and long-range force correction (LFC)
    $r^\ast_c = 2.5$ are investigated.  }
  \label{fig:tmp9}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.90\textwidth]{error-rcut-ball.eps} 
  \includegraphics[width=0.90\textwidth]{error-rcut.eps}
  \caption{(Color online)
    The colliding clusters (the first row), the RMS force error
    distribution of uniform cut-off with $r_c^\ast = 5.0$ (the second
    row), the cut-off distribution of adaptive cut-off with $r_c^\ast
    = 5.0$ (the third row) and the magnitude of long-range force
    correction with $r_c^\ast = 2.5$ (the fourth row). The four
    columns corresponds to snap shots taken at $t^\ast = 12,\ 24,\
    36,\ 56$, respectively.  }
  \label{fig:tmp10}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{wy.eps}
  \caption{(Color online)
    The angular velocity of cluster $A$ versus time. Uniform
    cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
    $r_c = 5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$
    are investigated.}
  \label{fig:tmp11}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[]{ly.eps}
  \caption{(Color online)
    The angular moment of cluster $A$ versus time. Uniform
    cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
    $r_c = 5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$
    are investigated.}
  \label{fig:tmp12}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{cost.eps}
  \caption{(Color online)
    The computational cost versus time. Uniform
    cut-off (URC) $r_c^\ast = 2.5,\ 5.0,\ 7.5$, adaptive cut-off (ARC)
    $r_c = 5.0$ and long-range force correction (LFC) $r^\ast_c = 2.5$
    are investigated.}
  \label{fig:tmp13}
\end{figure}

@@

In this paper, we developed the force error estimate for non-bonded
short-range interactions in the inhomogeneous molecular systems. The
RMS force error can be expressed by a summation of a homogeneity
error, an inhomogeneity error and a correlation error. In the present
paper, we only considered the cases, in which the correlation error
does not dominate. In an inhomogeneous system, the basic observation
of the error distribution was that the homogeneity error dominates the
bulk material regions, whereas the inhomogeneity error dominates the
interfacial regions where the density changes within the length scale
of a few molecules. The inhomogeneity error can be more than one
order of magnitude larger than the homogeneity error.  Two methods
were proposed to improve the efficiency and accuracy of the
simulation. The adaptive cut-off method uses smaller cut-off radius
for the low-error bulk regions and larger cut-off radius for the
high-error interfacial regions, so that the RMS force error is
uniformly distributed over the simulation region. The long-range force
correction method corrects the force computation by the mean error
force, so that the inhomogeneity error is removed from the system.
It should be noticed that the porposed error estimate and correction
methods can only be used to periodic systems.

@@

{
  In the systems tested by the present paper, the computational
  load of the error estimate is small compared to that of the
  short-range interaction.
  However, it should be noticed that
  the cost of the error estimate scales as $\mathcal O(N\log N)$,
  which may become intractable when the $\mathcal O(N)$ scaling
  short-range system is extremely large, and eventually
  overwhelms the total computational cost as the
  system size grows to infinity.
  If the system also needs long-range electrostatic calculation
  that is usually treated by the $\mathcal O(N\log N)$ scaling
  Ewald type algorithms~\cite{darden1993pme, essmann1995spm, deserno1998mue1},
  the extra load of the error estimate is likely to be acceptable.
  We want to stress again the main research interest of the present paper is the
  error estimate, the proposed adaptive cut-off and long-range
  correction methods. The examples are used to demonstrate
  the validity of these theoretical results. The applications
  of the error estimate is more general than the studied examples,
  because we only assumed the interaction is short-ranged and
  treated by the cut-off method.
  Other kind the short-range interaction (not only the Lennard-Jones
  but also the Buckingham,
  the direct part of the Ewald family algorithms, etc.),
  and other kinds of inhomogeneity
  (not only  planar and merging spherical interfaces)
  can be easily studied by the error estimates and the proposed methods.
  However, it is impossible to test all possible cases within one paper.
  The error study of
  more realistic systems requires the error estimates of the long-range
  algorithms, and careful comparisons with the short-range error.
  Since the present paper is focusing on the short-range
  interactions, and the space is limited,
  they will be given in the future work.
}
